Deep Reinforcement Learning \\ Actor-Critic and Trust region-based

### 2020-12-29 Paper/Paper.tex
Actor critic pseudo code

\usepackage{graphicx}
\usepackage{amsmath}

@@

\begin{equation*}
\resizebox{.95\linewidth}{!}{%
  $\begin{split}
    \nabla J({\boldsymbol{\theta}}) &\propto
    \sum_{s_t \in \mathcal{S}} \mu (s_t) \sum_{a_t \in \mathcal{A}} Q_{\pi_{\boldsymbol{\theta}}}(s_t,a_t) \nabla \pi (a_t|s_t; \boldsymbol{\theta}) \\
    &=\sum_{s_t \in \mathcal{S}} \mu (s_t) \sum_{a_t \in \mathcal{A}} \pi (a_t|s_t; \boldsymbol{\theta}) Q_{\pi_{\boldsymbol{\theta}}}(s_t,a_t) \frac{\nabla \pi (a_t|s_t; \boldsymbol{\theta})}{\pi (a_t|s_t; \boldsymbol{\theta})} \\
    &=\sum_{s_t \in \mathcal{S}} \mu (s_t) \sum_{a_t \in \mathcal{A}} \pi (a_t|s_t; \boldsymbol{\theta}) Q_{\pi_{\boldsymbol{\theta}}}(s_t,a_t) \nabla \log{\pi (a_t|s_t; \boldsymbol{\theta})} \\
    &= \mathbb{E}[Q_{\pi_{\boldsymbol{\theta}}}(S_t,A_t) \nabla \log{\pi (A_t|S_t; \boldsymbol{\theta})}] \\
    &= \mathbb{E}[G_t \nabla \log{\pi (A_t|S_t; \boldsymbol{\theta})}] \\
  \end{split}
  $}
\end{equation*}

\noindent where $\mathbb{E}$ is the expectation over the distribution of states $\mu(s_t)$ and actions $\pi (a_t|s_t; \boldsymbol{\theta})$; $A_t$ and $S_t$ are random variables ($A_t \sim \mu(s_t)$ and $S_t \sim \pi (a_t|s_t; \boldsymbol{\theta})$); and $Q_{\pi_{\boldsymbol{\theta}}}(S_t,A_t)$ can be replaced by $G_t$ since $\mathbb{E}[G_t| S_t,A_t] = Q_{\pi_{\boldsymbol{\theta}}}(S_t,A_t)$.

@@

@@

We denote the \emph{Expected Cumulative Reward} as $J(\boldsymbol{\theta})$, since we seek to maximize it depending on the parameters of the policy $\pi_{\boldsymbol{\theta}}$. Therefore, we can use \emph{Gradient ascent} in $J$ to maximize the performance of the policy:
\begin{equation}
  \boldsymbol{\theta}_{t+1} = \boldsymbol{\theta}_{t} + \alpha \nabla J(\boldsymbol{\theta}_t)
\end{equation}

>>>>

\usepackage[]{algorithm2e}
\usepackage{graphicx}
\usepackage{amsmath}

@@

\begin{equation*}
\resizebox{.95\linewidth}{!}{%
  $\begin{split}
    \nabla J({\boldsymbol{\theta}}) &\propto
    \sum_{s_t \in \mathcal{S}} \mu (s_t) \sum_{a_t \in \mathcal{A}} Q_{\pi_{\boldsymbol{\theta}}}(s_t,a_t) \nabla \pi (a_t|s_t; \boldsymbol{\theta}) \\
    &=\sum_{s_t \in \mathcal{S}} \mu (s_t) \sum_{a_t \in \mathcal{A}} \pi (a_t|s_t; \boldsymbol{\theta}) Q_{\pi_{\boldsymbol{\theta}}}(s_t,a_t) \frac{\nabla \pi (a_t|s_t; \boldsymbol{\theta})}{\pi (a_t|s_t; \boldsymbol{\theta})} \\
    &=\sum_{s_t \in \mathcal{S}} \mu (s_t) \sum_{a_t \in \mathcal{A}} \pi (a_t|s_t; \boldsymbol{\theta}) Q_{\pi_{\boldsymbol{\theta}}}(s_t,a_t) \nabla \log{\pi (a_t|s_t; \boldsymbol{\theta})} \\
    &= \mathbb{E}_{s \sim \mu_{\pi}, a \sim \pi_{\theta}}[Q_{\pi_{\boldsymbol{\theta}}}(S_t,A_t) \nabla \log{\pi (A_t|S_t; \boldsymbol{\theta})}] \\
    &= \mathbb{E}_{s \sim \mu_{\pi}, a \sim \pi_{\theta}}[G_t \nabla \log{\pi (A_t|S_t; \boldsymbol{\theta})}] \\
  \end{split}
  $}
\end{equation*}

\noindent where $\mathbb{E}_{s \sim \mu_{\pi}, a \sim \pi_{\theta}}$ is the expectation of both state and action distributions following the policy $\pi_{\boldsymbol{\theta}}$; $A_t$ and $S_t$ are random variables ($A_t \sim \mu_{\pi}$ and $S_t \sim \pi_{\theta}$); and $Q_{\pi_{\boldsymbol{\theta}}}(S_t,A_t)$ can be replaced by $G_t$ since $\mathbb{E}[G_t| S_t,A_t] = Q_{\pi_{\boldsymbol{\theta}}}(S_t,A_t)$.

@@

%\resizebox{.95\linewidth}{!}{%
\begin{algorithm}[h]
 \textbf{Input}: differentiable policy and state-value function parameterization $\pi(a|s;\boldsymbol{\theta})$ and $V(s;|s;\boldsymbol{w})$\;
 \textbf{Parameters}: step sizes $\alpha^{\boldsymbol{\theta}}>0,\  \alpha^{\boldsymbol{w}}>0$ and discount factor $\gamma \in [0,1]$\;
 Initialize policy and state-value parameters $\boldsymbol{\theta}\in\mathbb{R}^d$ and $\boldsymbol{w}\in\mathbb{R}^{d'}$\;
 \For{Episode = 1, 2, ...}{
  \While{$S_t$ is not terminal (for each time step $t$)}{
    Sample action $A_t \sim \pi(\cdot|S_t;\boldsymbol{\theta})$ \;
    Take action $A_t$ and observe $S_{t+1}, R_{t+1}$\;
    \If{$S_{t+1}$ is terminal}{
      $V(S_{t+1}; \boldsymbol{w}) = 0$\;
    }
    $\delta \gets R_{t+1} + \gamma V(S_{t+1}; \boldsymbol{w}) - V(S_{t}; \boldsymbol{w})$\;
    $\boldsymbol{w} \gets \boldsymbol{w} + \alpha^{\boldsymbol{w}} \delta \nabla V(S_{t}; \boldsymbol{w})$\;
    $\boldsymbol{\theta} \gets \boldsymbol{\theta} + \alpha^{\boldsymbol{\theta}} \delta \nabla \log{\pi(A_{t}|S_{t}; \boldsymbol{\theta})}$\;
    $S_t \gets S_{t+1}$\;
  }
 }
 \caption{Advantage Actor Critic pseudocode \cite{Sutton1998}.}
\end{algorithm}
%}

One down side of policy gradient methods is that they can ha

@@
